---
title: "p8105_hw5_wq2161"
author: "Wanxin Qi"
date: "11/14/2021"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1


## Problem 2

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time. Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r long_study, message = FALSE}
empty_df = 
  tibble(
    file_name = list.files("data", full.names = TRUE)
  )

read_df = function(path) {
  file_data = read_csv(path)
}

long_study = 
  empty_df %>%
  mutate(
    data_value = purrr::map(pull(empty_df, file_name), read_df),
    file_name = substr(file_name, 6, 11)
  ) %>%
  unnest(cols = data_value)

long_study =
  long_study %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "data_value"
  ) %>%
  mutate(
    week = substr(week, 6, 6),
    week = as.integer(week),
    subject_arm = substr(file_name, 1, 3)
  ) %>%
  rename(subject_id = file_name) %>%
  relocate(subject_arm, subject_id) %>%
  mutate(
    subject_arm = factor(subject_arm, levels = c("con", "exp"), ordered = FALSE)
  )

long_study

long_study %>%
  ggplot(aes(x = week, y = data_value, color = subject_id)) +
  geom_line(alpha = .5) +
  labs(
    title = "Observations On Each Subject Over Time",
    x = "Week",
    y = "Data"
  )
```


## Problem 3

Write a function that takes a vector as an argument; replaces missing values using the rules defined; returns the resulting vector.

* For numeric variables, you should fill in missing values with the mean of non-missing values

* For character variables, you should fill in missing values with "virginica"

Apply this function to the columns of iris_with_missing using a map statement.

```{r iris_with_missing}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

refill_missing_value = function(column) {
  
  if (is.numeric(column)) {
    column = replace_na(column, round(mean(column, na.rm = TRUE), digits = 1))
  }
  
  if (is.character(column)) {
    column = replace_na(column, "virginica")
  }
  
  return(column)
  
}

iris_refill_missing = map(iris_with_missing, refill_missing_value)

iris_with_missing =
  tibble(
    Sepal.Length = iris_refill_missing[["Sepal.Length"]],
    Sepal.Width = iris_refill_missing[["Sepal.Width"]],
    Petal.Length = iris_refill_missing[["Petal.Length"]],
    Petal.Width = iris_refill_missing[["Petal.Width"]],
    Species = iris_refill_missing[["Species"]]
  )

iris_with_missing
```

