---
title: "p8105_hw5_wq2161"
author: "Wanxin Qi"
date: "11/14/2021"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Describe the raw data.

```{r homicide_df, message = FALSE}
homicide_df = read_csv("data/homicide-data.csv", na = c("", "Unknown"))

head(homicide_df)
```

The dataset includes the data on homicides in 50 large U.S. cities gathered by the Washington Post. It contains `r ncol(homicide_df)` variables, which are `r colnames(homicide_df)`, and `r nrow(homicide_df)` observations.

Create a city_state variable and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides.

```{r homicide_summary, message = FALSE}
homicide_df =
  homicide_df %>%
  mutate(city_state = str_c(city, state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest"        ~ "unsolved",
           disposition == "Closed by arrest"      ~ "solved",
         )) %>%
  relocate(city_state) %>%
  filter(city_state != "TulsaAL")

homicide_summary = 
  homicide_df %>%
    select(-city, -state) %>%
    group_by(city_state) %>%
    summarize(
      n_unsolved = sum(resolution == "unsolved"),
      n_homicide = n()
    )

homicide_summary
```

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r baltimore_test}
baltimore_df =
  homicide_df %>%
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>%
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )

baltimore_test = 
  prop.test(
    x = baltimore_summary %>% pull(unsolved),
    n = baltimore_summary %>% pull(n))

baltimore_test %>%
  broom::tidy() %>%
  select(estimate, starts_with("conf"))
```

Run prop.test for each of the cities in the dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of `purrr::map`, `purrr::map2`, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

```{r results_df}
prop_test_function = function(city_df) {
  
  city_summary = 
    city_df %>%
      summarize(
        unsolved = sum(resolution == "unsolved"),
        n = n()
      )

  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n))
  
  return(city_test)
  
}

results_df =
  homicide_df %>%
  nest(data = uid:resolution) %>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))

results_df
```

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r results_df_plot}
results_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    title = "The Estimates and CIs For Each City",
    x = "City State",
    y = "Estimated proportion of Unsolved Homicide"
  )
```


## Problem 2

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time. Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r long_study, message = FALSE}
empty_df = 
  tibble(
    file_name = list.files("data/p2", full.names = TRUE)
  )

read_df = function(path) {
  file_data = read_csv(path)
}

long_study = 
  empty_df %>%
  mutate(
    data_value = purrr::map(pull(empty_df, file_name), read_df),
    file_name = substr(file_name, 9, 14)
  ) %>%
  unnest(cols = data_value)

long_study =
  long_study %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "data_value"
  ) %>%
  mutate(
    week = substr(week, 6, 6),
    week = as.integer(week),
    subject_arm = substr(file_name, 1, 3)
  ) %>%
  rename(subject_id = file_name) %>%
  relocate(subject_arm, subject_id) %>%
  mutate(
    subject_arm = factor(subject_arm, levels = c("con", "exp"), ordered = FALSE)
  )

long_study

long_study %>%
  ggplot(aes(x = week, y = data_value, color = subject_id)) +
  geom_line(alpha = .5) +
  geom_point(aes(shape = subject_arm), size = 1.5, alpha = .5) +
  labs(
    title = "Observations On Each Subject Over Time",
    x = "Week",
    y = "Data"
  ) + 
  theme(
    legend.box = "vertical",
    legend.key.size = unit(0.5, "pt"),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8)
  )
```

Based on the spaghetti plot, the data value of experimental group is generally greater than control group.


## Problem 3

Write a function that takes a vector as an argument; replaces missing values using the rules defined; returns the resulting vector.

* For numeric variables, you should fill in missing values with the mean of non-missing values

* For character variables, you should fill in missing values with "virginica"

Apply this function to the columns of iris_with_missing using a map statement.

```{r iris_with_missing}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

refill_missing_value = function(column) {
  
  if (is.numeric(column)) {
    column = replace_na(column, round(mean(column, na.rm = TRUE), digits = 1))
  }
  
  if (is.character(column)) {
    column = replace_na(column, "virginica")
  }
  
  return(column)
  
}

iris_refill_missing = map(iris_with_missing, refill_missing_value)

iris_without_missing =
  tibble(
    Sepal.Length = iris_refill_missing[["Sepal.Length"]],
    Sepal.Width = iris_refill_missing[["Sepal.Width"]],
    Petal.Length = iris_refill_missing[["Petal.Length"]],
    Petal.Width = iris_refill_missing[["Petal.Width"]],
    Species = iris_refill_missing[["Species"]]
  )

iris_without_missing
```

